Hypertension and microbiome

### 2019-08-28 articletwo-sensitivityanalysis.Rmd
Revert "Deseq2"
This reverts commit b47c65788968223cf674043ebbb895a53b7e1867.

@@

```{r Import previous session}
load(paste0("session/", sort(list.files("session"), decreasing = TRUE)[1]))
```

@@

```{r my variables}
var.CL.opt <- c("BL_AGE", "SEX", "BMI", "CURR_SMOKE", "Q57X", "PREVAL_DIAB", "BP_TREAT")
```

@@

betadiversity.askbp <- calculate.betadiversity(pseq = pseq.species,
                                                matrix = bray.dist.m.species,
                                                vars = list("max" = var.CL.opt,
                                                            "min" = var.CL.min),
                                               npermutations = 999)

diversities.helthy <- mergediversities(alphadiversity.askbp,
                                       betadiversity.askbp,
                                       names.dset = names.dset)

@@

Subjects with diabetes, cancer, kidney disease, and coronary disease are dropped.

@@

betadiversity.healthy <- calculate.betadiversity(pseq = pseq.species.healthy,
                                                matrix = bray.dist.m.species.healthy,
                                                vars = list("max" = var.CL[var.CL != "PREVAL_DIAB"],
                                                            "min" = var.CL.min),
                                                npermutations = 999)

diversities.helthy <- mergediversities(alphadiversity.healthy,
                                       betadiversity.healthy,
                                       names.dset = names.dset)

@@

betadiversity.normalweight <- calculate.betadiversity(pseq = pseq.species.normalweight,
                                                matrix = bray.dist.m.species.normalweight,
                                                vars = list("max" = var.CL[var.CL != "BMI"],
                                                            "min" = var.CL.min),
                                                npermutations = 999)

diversities.helthy <- mergediversities(alphadiversity.normalweight,
                                       betadiversity.normalweight,
                                       names.dset = names.dset)

@@

betadiversity.obese <- calculate.betadiversity(pseq = pseq.species.obese,
                                                matrix = bray.dist.m.species.obese,
                                                vars = list("max" = var.CL[var.CL != "BMI"],
                                                            "min" = var.CL.min),
                                               npermutations = 999)

diversities.helthy <- mergediversities(alphadiversity.obese,
                                       betadiversity.obese,
                                       names.dset = names.dset)

@@

>>>>

### RR biome functions

<details>
  <summary>Open/Close</summary>

```{r RR biome functions, code=readLines("articletwo-rrbiome.R")}
source("articletwo-rrbiome.R")
```

</details>

### Plot functions

<details>
  <summary>Open/Close</summary>

```{r Plot functions, code=readLines("articletwo-ggplot.R")}
source("articletwo-ggplot.R")
```

</details>

@@

```{r Import previous session}
pseq.species <- import_filter_data("data/phfinrisk_centrifuge_species_all_drop50k_2018-11-30_2019-06-03.RDs")
bray.dist.m.species  <- readRDS("rds-20190828/bray.dist.m.species.rds")
names.dset <- getdescriptions()
```

@@

```{r my variables}
var.BP <- c("MAP", "SYSTM", "DIASM", "PULSEPRESSURE", "HYPERTENSION")
var.CL.min <- c("BL_AGE", "SEX")
var.CL <- c("BL_AGE", "SEX", "BMI", "CURR_SMOKE", "Q57X", "PREVAL_DIAB",
            "BL_USE_RX_C03","BL_USE_RX_C07", "BL_USE_RX_C08", "BL_USE_RX_C09")
var.CL.opt <- c("BL_AGE", "SEX", "BMI", "CURR_SMOKE", "Q57X", "PREVAL_DIAB", "BP_TREAT")
permutations <- 3
```

@@

betadiversity.askbp <- calculate.betadiversity(pseq = pseq.species,
                                                matrix = bray.dist.m.species,
                                                vars = list("max" = var.CL.opt,
                                                            "min" = var.CL.min),
                                               npermutations = permutations)

diversities.askbp <- mergediversities(alphadiversity.askbp,
                                       betadiversity.askbp,
                                       names.dset = names.dset)

@@

Subjects with diabetes, cancer, and coronary disease are dropped. No
easy variable was found for kidney disesase.

@@

betadiversity.healthy <- calculate.betadiversity(pseq = pseq.species.healthy,
                                                matrix = bray.dist.m.species.healthy,
                                                vars = list("max" = var.CL[var.CL != "PREVAL_DIAB"],
                                                            "min" = var.CL.min),
                                                npermutations = permutations)

diversities.healthy <- mergediversities(alphadiversity.healthy,
                                       betadiversity.healthy,
                                       names.dset = names.dset)

@@

betadiversity.normalweight <- calculate.betadiversity(pseq = pseq.species.normalweight,
                                                matrix = bray.dist.m.species.normalweight,
                                                vars = list("max" = var.CL[var.CL != "BMI"],
                                                            "min" = var.CL.min),
                                                npermutations = permutations)

diversities.normalweight <- mergediversities(alphadiversity.normalweight,
                                       betadiversity.normalweight,
                                       names.dset = names.dset)

@@

betadiversity.obese <- calculate.betadiversity(pseq = pseq.species.obese,
                                                matrix = bray.dist.m.species.obese,
                                                vars = list("max" = var.CL[var.CL != "BMI"],
                                                            "min" = var.CL.min),
                                               npermutations = permutations)

diversities.obese <- mergediversities(alphadiversity.obese,
                                       betadiversity.obese,
                                       names.dset = names.dset)

@@

```{r save session}
save.image(file = "session/session-sensitivity.Rdata")
```
